### 2022-02-24 draft2.tex
rough draft of sections 1, 2 and 3

\begin{flushleft}
    \begin{adjustwidth}{-3cm}{-1cm}
    \begin{tabular}{ | p{2.4cm} | p{2cm} | p{4cm} | p{3cm} | l |}
    \hline
    Representation & Scoring & Flexibility/Information & Ensemble &
    Storage Requirement
    \\ \hline

    Parametric & All methods & Limited to common distribution families 
    &  & Low 3-6 values \\ \hline

    Discretized bins & All methods, more computation required for some (CRPS) &
    Any shape allowed, but limited to bin description and range & &
    High
    \\ \hline

    Samples & Limited to CRPS and IS unless smoothing is performed & High & & 
    Very high, thousands of values
    \\ \hline

    Quantiles & IS, WIS & High & & Medium 
    \\ \hline

    Discrete Mixture & All methods, but may be limited by computation & 
    High with proper approximation &
    & Low-Medium
    \\ \hline

>>>>

\begin{flushleft}
    \begin{adjustwidth}{-3cm}{-1cm}
    \begin{tabular}{ | p{2.4cm} | p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
    \hline
    Representation & Scoring & Flexibility/Information & Ensemble &
    Storage Requirement
    \\ \hline

    Parametric & LogS, CRPS, IS & Limited to common distribution families. 
    Infinite resoution
    & BMA & Low 3-6 values/prediction \\ \hline

    Samples & CRPS and IS. LogS after smoothing & Any shape. Resolution may be
    high but depends on sample size & BMA after smoothing. Resampling otherwise& 
    Hundreds or thousands of values/prediction
    \\ \hline

    Discretized bins & LogS, CRPS, IS &
    Any shape allowed, but limited by binning scheme & BMA &
    Depends on binning scheme but dozens to hundreds of values
    \\ \hline

    Quantiles & IS, WIS & Shape unknown but may still have much info with 
    enough quantiles. No tail information & Quantile averaging & Depends on 
    quantiles requested but dozens of values
    \\ \hline

    Discrete Mixture & LogS, CRPS, IS. May be more limited by computation & Can
    take on many shapes/approximate most & BMA 
    & 3 to limit values permitted
    \\ \hline
